### 2019-09-05 ic-journal/response-letter.tex

\item \begin{quote}
    L361 "Many lemmas ... contexts" this is a bit vague
  \end{quote}

  Rephrased: ``Many lemmas about above concepts (\texttt{CONTEXT}, \texttt{WG},
  \texttt{SEQ}, etc.)''

\item \begin{quote}
    L374 "An highlight"
  \end{quote}
  Fixed. Now we say ``One highlight...''.

\item \begin{quote}
    L378 "is a" => "are"
  \end{quote}
  Fixed. ``... what kind of binary relations on CCS process are (strong) bisimulations.''

\item \begin{quote}
    L385 "With *the* above"
  \end{quote}
  Fixed.

\item \begin{quote}
    L386 "the definition" of what? (bisimilarity, but say that)
  \end{quote}
  Fixed (``the definition of (strong) bisimilarity``).

\item \begin{quote}
    L394 "since *the* Kananaskis-11 release"
  \end{quote}
  Fixed.

\item \begin{quote}
    L396 "we call *the* Hol_coreln"
  \end{quote}
  Fixed.

\item \begin{quote}
    L410 $E$ and $E'$ missing
  \end{quote}
  All formal theorems and definitions are generated from HOL4.
  By default, all theorems are fully specialised, removing outermost
  universal quantifiers. For certain important theorems like this one,
  now we have disabled the specialization showing outermost
  universal quantifiers.

@@

\item \begin{quote}
    L436 "is defined upon weak transition" grammar
  \end{quote}

  Rephrased: ``The definition of weak bisimulation is based on weak
  and $\epsilon$--transitions:''

\item \begin{quote}
    L505 this is good: it is missing for strong bisimilarity, should
    be added there too (the two definitions are now not explicitly
    related)
  \end{quote}
TODO (remove the duplicated part of weak bisimulation, mergin into the
strong case).

\item \begin{quote}
    L580 "a contraction" ?
  \end{quote}
  This is no big problem here, as we are talking about any relation
  (which is a contraction) is not in general a bisimulation. However
  we have removed the word ``a'', having just: ``contraction does not imply weak bisimulation, ...''

\item \begin{quote}
    section 4.6 header: "the formalisation of bisimulation up to
    bisimilarity", i would say; also since you're not using
    compatible/respectful functions
  \end{quote}
  Fixed.

\item \begin{quote}
    L599 PRQ not so pretty spacing. perhaps mention around here that
    naive weak bisimulation up to weak bisimilarity is unsound?
  \end{quote}
  Fixed PRQ; Mentioned ``naive weak bisimulation up to weak
  bisimilarity is unsound'' right before the definition of ``weak
  bisimilation up to.''

\item \begin{quote}
    L655 (around here): i'd say in the text above it that this is a
    different bisimulation game, not a different up-to technique
  \end{quote}
  Thanks. We have added ``we actually used a different bisimulation game defined below''.

\item \begin{quote}
    L708 " closure of bisimilarity under such operator" not sure whether this is gramatically correct
  \end{quote}
  Rephrased: `` we also consider the relation closure of bisimilarity
  w.r.t. summation...''

@@

\item \begin{quote}
    Overall, in section 4.7, it seems the claim in the beginning is
    only proved under certain hypotheses: the "free-action" property,
    or in the Glabbeek proof, finite processes. This is all very much
    hidden: and it should be said up-front what we are going to prove
    exactly under which assumptions.
  \end{quote}

  TODO

\item \begin{quote}
    L740 "this proof" which? 
  \end{quote}

  ``this proof (Theorem~\ref{thm:coarsestfiniteState} in next
  section)``.

@@

\item \begin{quote}
    You assume the reader knows what Hol_reln is, but this not always the case. 
Then, you define the congruence in terms of the equivalence, but is
the equivalence already defined somewhere?
  \end{quote}

  TODO

\item \begin{quote}
    The argument at lines 387-389 is clear only after the lines 394-427 have been read.
  \end{quote}

  TODO (merge strong and weak cases0

\item \begin{quote}
    At lines 577 you write that proving properties for contraction is
    in general harder than proving properties for expansion. Could you
    explain why?
  \end{quote}

  We added a few more words right after: ``this is mostly due to the surprising fact
that, contraction does not imply weak bisimulation (while expansion
indeed implies weak bisimulation) ''.

### 2019-09-05 ic-journal/coarsest.tex
Stage work revising the IC paper

The coarsest congruence
contained in (weak) bisimilarity, namely \emph{bisimilarity
  congruence}, is
the \emph{composition closure} (\texttt{CC}) of (weak) bisimilarity:
\begin{alltt}
\HOLConst{WEAK_CONGR} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{CC} \HOLConst{WEAK_EQUIV}\hfill{[WEAK_CONGR]}
\HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}. \HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \ensuremath{(}\HOLBoundVar{c} \HOLBoundVar{g}\ensuremath{)} \ensuremath{(}\HOLBoundVar{c} \HOLBoundVar{h}\ensuremath{)}\ensuremath{)}\hfill{[CC_def]}
\end{alltt}
 (We need not  put $R\ g\ h$ in the antecedent of
  \texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.)
For any relation $R$ 
on CCS processes, the composition closure of $R$ is always at least as
fine as $R$
(here $\subseteq_r$ stands for \emph{relational subset})
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}. \HOLConst{CC} \HOLBoundVar{R} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R}\hfill{[CC_is_finer]}
\end{alltt}
Furthermore, we prove that any (pre)congruence contained in $R$ (which
itself may not be) is contained in the composition closure of $R$
(hence the closure is the coarsest one):
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \HOLBoundVar{R\sp{\prime}}. \HOLConst{congruence} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[CC_is_coarsest]}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \HOLBoundVar{R\sp{\prime}}. \HOLConst{precongruence} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[PCC_is_coarsest]}
\end{alltt}

Given the central role of the  
 sum operator, we also consider the closure of bisimilarity under such
 operator, called \emph{equivalence compatible with sums}
(\texttt{SUM_EQUIV}): %%, denoted by $\approx^+$: (not used this symbol)
\begin{alltt}
\HOLConst{SUM_EQUIV} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}\hfill{[SUM_EQUIV]}
\end{alltt}

@@

\begin{figure}[ht]
\begin{displaymath}
\xymatrix@R=3ex{
{\textrm{Weak bisimilarity } (\approx)} & {\textrm{Equiv.
    compatible with sums (\texttt{SUM\_EQUIV})}} \ar@/^3ex/[ldd]^{\subseteq}\\
{\textrm{Bisimilarity congruence (\texttt{WEAK\_CONGR})}}
\ar[u]^{\subseteq} \ar[ru]^{\subseteq} \\
{\textrm{Rooted bisimilarity } (\rapprox)} \ar[u]^{\subseteq}
}
\end{displaymath}
\vspace{-2ex}
\caption{Relationship between the equivalences mentioned}
\label{fig:relationship}
\end{figure}

@@

There exists a different, more complex, proof of (\ref{eq:coarsest}),
given by van Glabbeek \cite{van2005characterisation}, which does not
require any additional assumption.
The core lemma says, for
any two processes $p$ and $q$, if there exists a \emph{stable} (i.e.~$\tau$-free)
 process $k$ which is not bisimilar with any derivative of $p$ and
 $q$, then \texttt{SUM_EQUIV} indeed implies rooted bisimilarity ($\rapprox$):
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
        \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}. \HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}. \HOLFreeVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}\hfill{[PROP3_COMMON]}
\end{alltt}
\begin{alltt}
\HOLConst{STABLE} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{p\sp{\prime}}. \HOLFreeVar{p} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{u} \HOLSymConst{\HOLTokenNotEqual{}} \HOLSymConst{\ensuremath{\tau}}\hfill{[STABLE]}
\end{alltt}
To construct this process $k$,
 the proof relies on arbitrary infinite sums of 
processes and uses transfinite induction to obtain
an arbitrary large sequence of processes (firstly introduced by Jan
Willem Klop \cite{van2005characterisation})
 that are all pairwise non-bisimilar.
We have partially formalised
this proof, because the typed logic
implemented in various HOL systems (including Isabelle/HOL) is not
strong enough to define a type for all possible ordinals
\cite{norrish2013ordinals}, thus
we have replaced transfinite induction with plain induction. As a
consequence, the final
result is about a restricted class of processes (which we have taken
to be the finite-state processes).
The proof, in the section below, uses extensively HOL's
\texttt{pred_set} theory \cite{melham1992hol}, with a mix
of CCS and pure mathematics.

@@

Combining the above lemma with \texttt{PROP3_COMMON} and \texttt{COARSEST_CONGR_RL},
we can  prove the following theorem for finite-state CCS:
\begin{theorem}{(Coarsest congruence contained in $\approx$ for
    finite-state CCS)}
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}\hfill[COARSEST_CONGR_FINITE]
\end{alltt}
\end{theorem}

>>>>

The coarsest congruence
contained in (weak) bisimilarity, namely \emph{bisimilarity
  congruence}, is
the \emph{composition closure} (\texttt{CC}) of (weak) bisimilarity:
\begin{alltt}
   \HOLConst{WEAK_CONGR} \HOLSymConst{\HOLTokenDefEquality{}} \HOLConst{CC} \HOLConst{WEAK_EQUIV}\hfill{[WEAK_CONGR]}
   \HOLConst{CC} \HOLFreeVar{R} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{g} \HOLBoundVar{h}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{c}. \HOLConst{CONTEXT} \HOLBoundVar{c} \HOLSymConst{\HOLTokenImp{}} \HOLFreeVar{R} \ensuremath{(}\HOLBoundVar{c} \HOLBoundVar{g}\ensuremath{)} \ensuremath{(}\HOLBoundVar{c} \HOLBoundVar{h}\ensuremath{)}\ensuremath{)}\hfill{[CC_def]}
\end{alltt}
We do not need to put $R\ g\ h$ in the antecedent of
  \texttt{CC\_def}, as this is anyhow obtained from the trivial context $(\lambda x.\,x)$.
For any \hl{binary} relation $R$ 
on CCS processes, the composition closure of $R$ is always at least as
fine as $R$
(here $\subseteq_r$ stands for \emph{relational subset})
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R}. \HOLConst{CC} \HOLBoundVar{R} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R}\hfill{[CC_is_finer]}
\end{alltt}
Furthermore, we prove that any (pre)congruence contained in $R$ (which
itself may not be) is contained in the composition closure of $R$
(hence the closure is the coarsest one):
\begin{alltt}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \HOLBoundVar{R\sp{\prime}}. \HOLConst{congruence} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[CC_is_coarsest]}
\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \HOLBoundVar{R\sp{\prime}}. \HOLConst{precongruence} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{R\sp{\prime}} \HOLSymConst{\HOLTokenRSubset{}} \HOLConst{CC} \HOLBoundVar{R}\hfill{[PCC_is_coarsest]}
\end{alltt}

Given the central role of the  
 summation, we also consider the relation closure of bisimilarity
 w.r.t. summation, called \emph{equivalence compatible with summation}
(\texttt{SUM_EQUIV}): %%, denoted by $\approx^+$: (not used this symbol)
\begin{alltt}
   \HOLConst{SUM_EQUIV} \HOLSymConst{\HOLTokenDefEquality{}} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{p} \HOLBoundVar{q}. \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLBoundVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}\hfill{[SUM_EQUIV]}
\end{alltt}

@@

\begin{figure}[ht]
\begin{displaymath}
\xymatrix{
{\textrm{Weak bisimilarity } (\approx)} & {\textrm{Equiv.
    compatible with summation (\texttt{SUM\_EQUIV})}}
\ar@/^3ex/[ldd]^{\supseteq\; ?}\\
{\textrm{Bisimilarity congruence (\texttt{WEAK\_CONGR})}}
\ar[u]^{\subseteq} \ar[ru]^{\subseteq} \\
{\textrm{Rooted bisimilarity } (\rapprox)} \ar[u]^{\subseteq}
}
\end{displaymath}
\caption{Relationships between several equivalences and $\wb$}
\label{fig:relationship}
\end{figure}

@@

There exists a different, more complex, proof of (\ref{eq:coarsest}),
given by van Glabbeek \cite{van2005characterisation}, which does not
require any additional assumption.
The core lemma says, for
any two processes $p$ and $q$, if there exists a \emph{stable} (i.e.~$\tau$-free)
 process $k$ which is not bisimilar with any derivative of $p$ and
 $q$, then \texttt{SUM_EQUIV} indeed implies rooted bisimilarity ($\rapprox$):
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{k}.
        \HOLConst{STABLE} \HOLBoundVar{k} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p\sp{\prime}} \HOLBoundVar{u}. \HOLFreeVar{p} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
        \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{q\sp{\prime}} \HOLBoundVar{u}. \HOLFreeVar{q} \HOLTokenWeakTransBegin\HOLBoundVar{u}\HOLTokenWeakTransEnd \HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenNeg{}}\ensuremath{(}\HOLBoundVar{q\sp{\prime}} \HOLSymConst{\HOLTokenWeakEQ} \HOLBoundVar{k}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q}\hfill{[PROP3_COMMON]}
\end{alltt}
\begin{alltt}
\HOLConst{STABLE} \HOLFreeVar{p} \HOLSymConst{\HOLTokenDefEquality{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \HOLBoundVar{p\sp{\prime}}. \HOLFreeVar{p} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \HOLBoundVar{p\sp{\prime}} \HOLSymConst{\HOLTokenImp{}} \HOLBoundVar{u} \HOLSymConst{\HOLTokenNotEqual{}} \HOLSymConst{\ensuremath{\tau}}\hfill{[STABLE]}
\end{alltt}
To construct this process $k$,
 the proof relies on arbitrary infinite sums of 
processes and uses transfinite induction to obtain
an arbitrary large sequence of processes (firstly introduced by Jan
Willem Klop \cite{van2005characterisation})
 that are all pairwise non-bisimilar.
We have only partially formalised
this proof (Theorem~\ref{thm:coarsestfiniteState} in next section), because ``the typed logic
implemented in various HOL systems (including Isabelle/HOL) is not
strong enough to define a type for all possible
ordinals''~\cite{norrish2013ordinals}.
\hl{As a consequence, the final result is only for finite-state
  CCS---a very restricted class.}

@@

Combining the above lemma with \texttt{PROP3_COMMON} and \texttt{COARSEST_CONGR_RL},
we can  prove the following theorem for finite-state CCS:
\begin{theorem}{(Coarsest congruence contained in $\approx$ for
    finite-state CCS)}
  \label{thm:coarsestfiniteState}
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{finite_state} \HOLFreeVar{p} \HOLSymConst{\HOLTokenConj{}} \HOLConst{finite_state} \HOLFreeVar{q} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLFreeVar{p} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{q} \HOLSymConst{\HOLTokenEquiv{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{r}. \HOLFreeVar{p} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r} \HOLSymConst{\HOLTokenWeakEQ} \HOLFreeVar{q} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{r}\ensuremath{)}\hfill[COARSEST_CONGR_FINITE]
\end{alltt}
\end{theorem}

### 2019-09-05 ic-journal/contraction.tex
Synchronized htex with tex files; clear all highlights
Stage work revising the IC paper

\subsection{Contractions}
\label{s:mcontr}

@@

In the first clause $Q$ is required to match $P$'s challenge
transition with at most one transition.
This makes sure that $Q$ is capable of mimicking $P$'s
work at least as efficiently as $P$. 
In contrast, the second clause of Definition~\ref{d:BisCon}, on the
challenges from $Q$, entirely ignores efficiency: it is the same
clause of  weak bisimulation~--- the final derivatives are even required
to be related  by $\wb$, rather than by $\R$.

Bisimilarity  contraction is coarser than 
 the \emph{expansion relation} 
$\expa$ \cite{arun1992efficiency,sangiorgi2015equations}.
This is a
preorder widely used in proof techniques for bisimilarity and that 
intuitively refines bisimilarity by 
 formalising the idea of `efficiency' between processes.
Clause (1) is the same in the two
preorders. But in clause (2) expansion uses 
$P \Arr \mu P'$, rather than $P \Arcap \mu P'$; 
 moreover with
contraction the final derivatives are simply required to be bisimilar.
An expansion 
$P \expa Q$
tells us  that $Q$ is always at least as efficient as $P$, whereas  the
 contraction $P \mcontrBIS Q$  just says that $Q$ has the  possibility of
being at least as efficient as $P$.

@@

As bisimilarity, so the expansion preorder is preserved by all operators but  sums.

@@

\hl{Like} (weak) bisimilarity and expansion, contraction is
preserved by all operators but (direct) sum.

>>>>

\subsection{Expansions and Contractions}
\label{s:mcontr}

@@

In the first clause $Q$ is required to match $P$'s challenge
transition with at most one transition.
This makes sure that $Q$ is capable of mimicking $P$'s
work at least as efficiently as $P$. 
In contrast, the second clause of Definition~\ref{d:BisCon}, on the
challenges from $Q$, entirely ignores efficiency: it is the same
clause of  weak bisimulation~---the final derivatives are even required
to be related  by $\wb$, rather than by $\R$.

Bisimilarity  contraction is coarser than 
 the \emph{expansion relation} $\expa$~\cite{arun1992efficiency,sangiorgi2015equations}.
This is a
preorder widely used in proof techniques for bisimilarity and that 
intuitively refines bisimilarity by 
 formalising the idea of `efficiency' between processes.
Clause (1) is the same in the two
preorders. But in clause (2) expansion uses 
$P \Arr \mu P'$, rather than $P \Arcap \mu P'$; 
 moreover with
contraction the final derivatives are simply required to be bisimilar.
An expansion 
$P \expa Q$
tells us  that $Q$ is always at least as efficient as $P$, whereas  the
 contraction $P \mcontrBIS Q$  just says that $Q$ has the possibility of
being at least as efficient as $P$.

@@

@@

Like the case of (weak) bisimilarity, the expansion and contraction
preorders are preserved by all CCS operators but the summation.

### 2019-09-05 ic-journal/intro.tex
Stage work revising the IC paper

Another benefit of the formalisation is 
that we can take advantage of results about different 
equivalences and preorders that share similar proof structures.
%
% Examples are: the results that rooted bisimilarity and rooted contraction are,
% respectively, the coarsest congruence contained in weak bisimilarity 
% and the coarsest precongruence contained in the contraction preorder; 
% the result about unique solution of equations for weak bisimilarity that uses the
% contraction preorder as an auxiliary relation, and other unique solution results (e.g.~%
% the one for rooted in which
% the auxiliary relation is rooted contraction); various forms of enhancements of the bisimulation
% proof method (the `up-to' techniques).
%
% rephrased: (TODO: still hard to read --Chun)
\hl{Such structural simililarities can be found, for instance, in the
following cases: the proofs that rooted bisimilarity and rooted
contraction are, respectively, the coarsest congruence contained in
weak bisimilarity and the coarsest precongruence contained in the
contraction preorder; the proofs about unique solution of equations
for weak bisimilarity that uses the contraction preorder as an
auxiliary relation, and other unique solution results (e.g. the one
for rooted in which the auxiliary relation is rooted contraction); the
proofs about various forms of enhancements of the bisimulation proof
method (the `up-to' techniques).}
%
In these cases, moving between proofs there are only a few places in
which the HOL proof scripts have to be modified.
Then the successful termination of the proof gives us a guarantee that the proof is
complete and trustworthy, eliminating the risks 
of overlooking or missing details as in \emph{paper-and-pencil} proofs.

>>>>

Another benefit of the formalisation is 
that we can take advantage of results about different 
equivalences and preorders that share similar proof structures.
%
% Examples are: the results that rooted bisimilarity and rooted contraction are,
% respectively, the coarsest congruence contained in weak bisimilarity 
% and the coarsest precongruence contained in the contraction preorder; 
% the result about unique solution(s) of equations for weak bisimilarity that uses the
% contraction preorder as an auxiliary relation, and other unique solution results (e.g.~%
% the one for rooted in which
% the auxiliary relation is rooted contraction); various forms of enhancements of the bisimulation
% proof method (the `up-to' techniques).
%
% rephrased: (TODO: still hard to read --Chun)
\hl{Such structural simililarities can be found, for instance, in the
following cases: the proofs that rooted bisimilarity and rooted
contraction are, respectively, the coarsest congruence contained in
weak bisimilarity and the coarsest precongruence contained in the
contraction preorder; the proofs about unique solution(s) of equations
for weak bisimilarity that uses the contraction preorder as an
auxiliary relation, and other unique solution results (e.g. the one
for rooted in which the auxiliary relation is rooted contraction); the
proofs about various forms of enhancements of the bisimulation proof
method (the `up-to' techniques).}
%
In these cases, moving between proofs there are only a few places in
which the HOL proof scripts have to be modified.
Then the successful termination of the proof gives us a guarantee that the proof is
complete and trustworthy, eliminating the risks 
of overlooking or missing details as in \emph{paper-and-pencil} proofs.
